Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-11-22 doc/Paper/main.tex
discussed self-calibration and KiDS

      \begin{figure}
        \begin{center}
          \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
          \caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
          \label{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods}
        \end{center}
      \end{figure}

>>>>

      The positive side of the enhanced sensitivity of galaxy clustering to photometric redshift uncertainties compared to cosmic shear is the possibility of using clustering measurements to self-calibrate some of these uncertainties. As an example, our analysis hints towards a consistently positive value of the relative shift parameters $\Delta z_i-\Delta z_j,\,i>j$ (see e.g. Figs. \ref{fig:constraints-pz-syst-auto+cross-vs-auto} and \ref{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}), i.e.: the different bins are more widely separated than their fiducial distributions assumes. Since the signal-to-noise ratio of cosmic shear measurements tends to increase towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions). Although the data analysed here are not yet sensitive enough to provide conclusive evidence of these types of systematics, larger samples will be able to provide useful insight on the presence of photometric redshift systematics.
      \begin{figure}
        \begin{center}
          \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
          \caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
          \label{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods}
        \end{center}
      \end{figure}
